Meaning of simple rules in investment strategies of algorithmic trading

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
zmieniona dokładność w tablekach do dwóch miejsc po przecinku

\section{The test results}
The study of strategy was carried out on the following markets:
\begin{itemize}
\item currency pairs: EURUSD, EURJPY, USDJPY, GBPUSD,
\item indexes: FUS500, BOSSAPLN,
\item commodities: FGOLD. FSILVER.
\end{itemize}
BOSSAPLN is currency index that represents ratio of PLN to four other currencies. Every currency pair used to calculate index has other weight USDPLN (40\%), EURPLN (50\%), GBPPLN (5\%), CHFPLN (5\%).
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for EURJPY} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 26.177 & 5.5909868 & 24 & 2764\\ \hline 
S1b & -14.774 & -0.67029627 & 6 & 2660\\ \hline 
S1c & 15.736 & 2.4898734 & 6 & 2332\\ \hline 
S1d & -4.57 & -0.47001954 & 21 & 2226\\ \hline 
S1s & 22.54 & 3.2459677 & Group of MA & 4975\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FSILVER} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & -5.31 & -0.64520049 & 81 & 2582\\ \hline 
S1b & 17.22 & 5.8571429 & 10 & 2508\\ \hline 
S1c & 4.17 & 0.55525965 & 10 & 2473\\ \hline 
S1d & 6.95 & 1.3314176 & 81 & 2336\\ \hline 
S1s & 21.96 & 5.5454545 & Group of MA & 4918\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for BOSSAPLN} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 5.87 & 1.9898305 & 21 & 2474\\ \hline 
S1b & 2.86 & 0.6059322 & 5 & 2416\\ \hline 
S1c & 10.91 & 4.3293651 & 5 & 2547\\ \hline 
S1d & -2.23 & -0.4247619 & 21 & 2502\\ \hline 
S1s & 17.91 & 4.3470874 & Group of MA & 4978\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FUS500} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 274.89 & 5.4433663 & 83 & 3200\\ \hline 
S1b & -70.94 & -0.47328041 & 15 & 2798\\ \hline 
S1c & 291.62 & 4.2584696 & 15 & 2186\\ \hline 
S1d & -106.67 & -0.73237212 & 82 & 1723\\ \hline 
S1s & 344.29 & 2.0821893 & Group of MA & 4916\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FGOLD} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 61.16 & 0.58503922 & 51 & 2578\\ \hline 
S1b & 227.58 & 2.8169328 & 5 & 2519\\ \hline 
S1c & 30.38 & 0.12023588 & 5 & 2470\\ \hline 
S1d & 248.21 & 1.5167125 & 51 & 2370\\ \hline 
S1s & 599.88 & 4.6027776 & Group of MA & 4948\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for GBPUSD} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 0.05736 & 1.061436 & 92 & 2588\\ \hline 
S1b & 0.12055 & 3.4101839 & 5 & 2513\\ \hline 
S1c & 0.15356 & 3.1116515 & 5 & 2475\\ \hline 
S1d & 0.01724 & 0.31254532 & 92 & 2319\\ \hline 
S1s & 0.36007 & 6.892611 & Group of MA & 4907\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for USDJPY} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 17.189 & 8.2362242 & 18 & 2693\\ \hline 
S1b & -9.802 & -0.73511324 & 54 & 2665\\ \hline 
S1c & 5.65 & 2.0582878 & 54 & 2280\\ \hline 
S1d & 1.867 & 0.60715447 & 18 & 2287\\ \hline 
S1s & 14.854 & 5.682479 & Group of MA & 4945\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

>>>>

\section{The test results}
The study of strategy was carried out on the following markets:
\begin{itemize}
\item currency pairs: EURUSD, EURJPY, USDJPY, GBPUSD,
\item indexes: FUS500, BOSSAPLN,
\item commodities: FGOLD. FSILVER.
\end{itemize}
BOSSAPLN is currency index that represents ratio of PLN to four other currencies. Every currency pair used to calculate index has other weight USDPLN (40\%), EURPLN (50\%), GBPPLN (5\%), CHFPLN (5\%).
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for EURJPY} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 26.18 & 5.59 & 24 & 2764\\ \hline 
S1b & -14.77 & -0.67 & 6 & 2660\\ \hline 
S1c & 15.74 & 2.49 & 6 & 2332\\ \hline 
S1d & -4.57 & -0.47 & 21 & 2226\\ \hline 
S1s & 22.54 & 3.25 & Group of MA & 4975\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FSILVER} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & -5.31 & -0.65 & 81 & 2582\\ \hline 
S1b & 17.22 & 5.86 & 10 & 2508\\ \hline 
S1c & 4.17 & 0.56 & 10 & 2473\\ \hline 
S1d & 6.95 & 1.33 & 81 & 2336\\ \hline 
S1s & 21.96 & 5.55 & Group of MA & 4918\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for BOSSAPLN} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 5.87 & 1.99 & 21 & 2474\\ \hline 
S1b & 2.86 & 0.61 & 5 & 2416\\ \hline 
S1c & 10.91 & 4.33 & 5 & 2547\\ \hline 
S1d & -2.23 & -0.42 & 21 & 2502\\ \hline 
S1s & 17.91 & 4.35 & Group of MA & 4978\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FUS500} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 274.89 & 5.44 & 83 & 3200\\ \hline 
S1b & -70.94 & -0.47 & 15 & 2798\\ \hline 
S1c & 291.62 & 4.26 & 15 & 2186\\ \hline 
S1d & -106.67 & -0.73 & 82 & 1723\\ \hline 
S1s & 344.29 & 2.08 & Group of MA & 4916\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FGOLD} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 61.16 & 0.59 & 51 & 2578\\ \hline 
S1b & 227.58 & 2.82 & 5 & 2519\\ \hline 
S1c & 30.38 & 0.12 & 5 & 2470\\ \hline 
S1d & 248.21 & 1.52 & 51 & 2370\\ \hline 
S1s & 599.88 & 4.60 & Group of MA & 4948\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for GBPUSD} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 0.06 & 1.06 & 92 & 2588\\ \hline 
S1b & 0.12 & 3.41 & 5 & 2513\\ \hline 
S1c & 0.15 & 3.11 & 5 & 2475\\ \hline 
S1d & 0.02 & 0.31 & 92 & 2319\\ \hline 
S1s & 0.36 & 6.89 & Group of MA & 4907\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for USDJPY} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline 
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline 
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline 
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline 
S1s & 14.85 & 5.68 & Group of MA & 4945\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier
